

%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Zhang Xuecheng} \\[7.5pt]
\href{https://github.com/zachz1016}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/xuecheng-zhang-29b0611b1/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{xuechengzhang1016@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ xuechengzhang1016@gmail.com} \ $|$ \ 
\href{tel:+86 81689638}{\raisebox{-0.05\height}\faMobile \ +65 81689638} \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{BSc, Computer Science(Big Data) at University Of Wollongong} & \hfill July 2020 - Mar 2023 \\[3.75pt]

\textbf{Diploma, Biomedical Engineering at Nanyang Polytechnic} & \hfill Apr 2015 - May 2017 \\[3.75pt] 

\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------
%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{FULL STACK DEVELOPER INTERN} & \hfill Aug 2022 - Feb 2023 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Involved in staff management app(ChuGo App) and inventory management system(Ops App) development, including the contract upload, contract management and digital signature functionalities utilizing Angular in Ionic Framework, PHP Laravel, and PostgreSQL for database.
        \item[--] Participated in Lexis Job development, a talent acquisition platform, utilizing React, NodeJS, and PostgreSQL. Smart recommendation and auto complete sentence functionalities. Design, develop, and implement high performance relational database tables for the application which successfully meet the needs of the company.
        \item[--] Conducted market researches and performed data analytic tasks with Excel, PostgreSQL and PowerBI to facilitate data visualisations and help executives make data-driven decisions. 
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{ASSISTANT OPERATING ENGINEER INTERN} & \hfill Mar 2017 - Jun 2017 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Manage the product entry and exit process by registering products, monitoring inventories, and tracking shipments.
        \item[--] Follow up with customers to ensure that all orders are fulfilled in a timely manner.  
        \item[--] Work with other departments to ensure that products are entered and shipped according to established procedures. 
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{X-ray Classification System} & \hfill \href{https://github.com/tanshihuai/X-Ray-Co}{Link to Github} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{A computer-aided diagnostic system that uses artificial intelligence to analyze and classify X-ray images using Python. It can accurately identify various diseases including Covid-19, pneumonia and pulmonary edema. The system is equipped with deep learning algorithms and utilizes a large data-set of X-ray images to train the model. The system can be used to improve diagnosis accuracy and reduce workload for radiologists. }  \\
\textbf{Restaurant Order System} & \hfill \href{https://github.com/kellock117/RestaurantOrderSystem}{Link to GitHub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{A system that was designed to provide customers with a fast and efficient way to order food using NodeJS, HTML5 and MongoDB. The system allows customers to order items easily and quickly, view their order status, and pay for the order. The order system also provides restaurant staff with a comprehensive view of all orders in real-time, and a daily, weekly and monthly basis turnover rate for the owner.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages: &  \normalsize{Python, JavaScript, Java, PHP, SQL}\\
Front-end Development: &  \normalsize{React, Angular, JQuery}\\
Database Platform and Applications: &  \normalsize{Hadoop, Hive, Spark, Pig Latin}\\  
Data Analysis Tools: &  \normalsize{Tableau, PowerBI, R Studio}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
